Covariance as constraint: Leveraging leaf economic relationships to constrain plant functional type trait estimates

### 2017-11-17 manuscript-md/03_results.Rmd
Clean up Makefile. Minor fig ref fix in results

We observed clear differences in the relative uncertainties of mean estimates with respect to sample size.
All of the high-latitude PFTs consistently had among the largest error bars around their mean estimates relative to other PFTs, while the traits with the largest uncertainties were dark respiration, $V_{c,max}$, and $J_{max}$.
For many of these trait-PFT combinations, the additional constraint from trait covariance provided by the multivariate and hierarchical models substantially reduced error bars, making it possible to compare estimates against those of other PFTs.
Our analysis of the relationship between model type, sample size, and estimate relative uncertainty found that this covariance-based constraint from the multivariate model becomes increasingly important at smaller sample sizes (\@ref(fig:civssamplesize)).
However, this analysis revealed no consistent significant benefit from the hierarchical model.

>>>>

We observed clear differences in the relative uncertainties of mean estimates with respect to sample size.
All of the high-latitude PFTs consistently had among the largest error bars around their mean estimates relative to other PFTs, while the traits with the largest uncertainties were dark respiration, $V_{c,max}$, and $J_{max}$.
For many of these trait-PFT combinations, the additional constraint from trait covariance provided by the multivariate and hierarchical models substantially reduced error bars, making it possible to compare estimates against those of other PFTs.
Our analysis of the relationship between model type, sample size, and estimate relative uncertainty found that this covariance-based constraint from the multivariate model becomes increasingly important at smaller sample sizes (Fig.\ \@ref(fig:civssamplesize)).
However, this analysis revealed no consistent significant benefit from the hierarchical model.
